Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-15 ms.tex
discussing proposal distribution

In our full-resolution fits, we use a MCMC approach to constrain the 
parameters $\tilde{I}_{545}$ and $T_2$. For each pixel, we run a 
Metropolis-Hastings Markov chain sampling the posterior probability of
reproducing the observed 217-3000 GHz SED as a function of the two parameters 
$\tilde{I}_{545}$ and $T_2$. More specifically, we are sampling the posterior 
given by:

@@

% justification for T2 prior standard deviation
With $\bar{T}_2$ = 15.7 K and $\sigma_{\bar{T}_2}$ = 1.4 K. The $T_2$ prior 
mean is chosen based on the typical high-latitude $T_2$ value derived from
the correlation slope analysis from $\S$\ref{sec:global}. We find, as 
desired, that this relatively broad $T_2$ prior has little influence on the 
derived temperatures, other than to regularize the rare pixels with one or more
defective intensities which might otherwise yield unreasonable parameter
estimates. In principle, there can also be an informative prior on 
$\tilde{I}_{545}$. However, we have chosen to assume a uniform prior on the SED
normalization and, as a matter of notation, will omit $P(\tilde{I}_{545})$ 
henceforward. In practice we always perform computations using logarithms of 
the relevant probabilities.
%mention something about the proposal distribution at some point?

@@

For each pixel, we initialize the Markov chain with parameters 
$\tilde{I}_{545}$ = $I_{545}$ and $T_2$ consistent with the FDS99 
DIRBE 100$\mu$m/240$\mu$m ratio map $\mathscr{R}$. We run 500 steps of burn-in 
and then 2000 steps during which we keep track of the proposed $T_{2, j}$ and 
$\tilde{I}_{545, j}$ values at the $j^{th}$ step since the end of burn-in. From
 these 2000 samples, we compute estimates of each parameter, 
$T_2$ = $\langle T_{2, j} \rangle$, $\tilde{I}_{545}$ = 
$\langle \tilde{I}_{545, j} \rangle$, and of each parameter's variance, 
$\sigma^2_{T_2}$ = $\langle T^2_{2, j} \rangle-\langle T_{2, j} \rangle ^2$ and
 $\sigma^2_{\tilde{I}_{545}}$=$\langle \tilde{I}^2_{545, j} 
\rangle-\langle \tilde{I}_{545, j} \rangle ^2$. We also compute the
 corresponding estimate of the monochromatic two-component intensity at 545 
GHz, $M_{545}$ = $\langle M_{545, j} \rangle$ = 
$\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}) \rangle$  and its variance. 
$M_{545}$ is of more general utility in making foreground predictions because 
it provides the normalization for the two-component spectrum $M_{\nu}$, 
independent of the \PLANCK~545 GHz bandpass. Lastly, we compute the 545 GHz
optical depth as $\tau_{545}$ = $\langle \tau_{545, j} \rangle$ = 
$\langle M_{545, j}/S_{545, j} \rangle$ and its variance, with the source 
function $S_{545}$ calculated according to Equation \ref{eqn:source}.

>>>>

In our full-resolution fits, we use a MCMC approach to constrain the 
parameters $\tilde{I}_{545}$ and $T_2$. For each pixel, we run a 
Metropolis-Hastings (MH) Markov chain sampling the posterior probability of
reproducing the observed 217-3000 GHz SED as a function of the two parameters 
$\tilde{I}_{545}$ and $T_2$. More specifically, we are sampling the posterior 
given by:

@@

With $\bar{T}_2$ = 15.7 K and $\sigma_{\bar{T}_2}$ = 1.4 K. The $T_2$ prior 
mean is chosen based on the typical high-latitude $T_2$ value derived from
the correlation slope analysis from $\S$\ref{sec:global}. We find, as 
desired, that this relatively broad $T_2$ prior has little influence on the 
derived temperatures, other than to regularize the rare pixels with one or more
defective intensities which might otherwise yield unreasonable parameter
estimates. In principle, there can also be an informative prior on 
$\tilde{I}_{545}$. However, we have chosen to assume a uniform prior on the SED
normalization and, as a matter of notation, will omit $P(\tilde{I}_{545})$ 
henceforward. In practice we always perform computations using logarithms of 
the relevant probabilities.
%mention something about the proposal distribution at some point?

@@

For each pixel, we initialize the Markov chain with parameters 
$\tilde{I}_{545}$ = $I_{545}$ and $T_2$ consistent with the FDS99 
DIRBE 100$\mu$m/240$\mu$m ratio map $\mathscr{R}$. The initial proposal 
distribution is a two-dimensional normal distribution, with 
$\sigma_{T_2}$=0.25 K and 
$\sigma_{\tilde{I}_{545}}$=max(0.01$\times$$I_{545}$, 0.05 MJy/sr). We run 5 
iterations of burn-in, each consisting of 500 MH steps. After each burn-in 
iteration, we rescale the proposal distribution so as to ultimately attain an 
acceptance fraction $f_{acc}$ as close as possible to the optimal value 
$f_{opt}=0.234$. This is accomplished by multiplying the proposal distribution 
standard deviations by $f_{acc}$/$f_{opt}$.

We then estimate the parameters and their covariances by performing 10000 steps
during which we keep track of the proposed $T_{2, j}$ and $\tilde{I}_{545, j}$ 
values at the $j^{th}$ step since the end of burn-in. From these 2000 samples, 
we compute estimates of each parameter, $T_2$ = $\langle T_{2, j} \rangle$, 
$\tilde{I}_{545}$ = $\langle \tilde{I}_{545, j} \rangle$, and of each 
parameter's variance, 
$\sigma^2_{T_2}$ = $\langle T^2_{2, j} \rangle-\langle T_{2, j} \rangle ^2$ and
$\sigma^2_{\tilde{I}_{545}}$=$\langle \tilde{I}^2_{545, j} 
\rangle-\langle \tilde{I}_{545, j} \rangle ^2$. We also compute the 
corresponding estimate of the monochromatic two-component intensity at 545 GHz,
$M_{545}$ = $\langle M_{545, j} \rangle$ = 
$\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}) \rangle$  and its variance. 
$M_{545}$ is of more general utility in making foreground predictions because 
it provides the normalization for the two-component spectrum $M_{\nu}$, 
independent of the \PLANCK~545 GHz bandpass. Lastly, we compute the 545 GHz
optical depth as $\tau_{545}$ = $\langle \tau_{545, j} \rangle$ = 
$\langle M_{545, j}/S_{545, j} \rangle$ and its variance, with the source 
function $S_{545}$ calculated according to Equation \ref{eqn:source}.
